Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-23 DGMM2025/paper.tex
adding visuals for visibility example and one example on the paper

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{environ}

@@

    In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
    coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
    of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
    visible using the same method as presented in \ref{fig:enter-label}.

@@

    Let $V$ the visibility around the point $p$, let $c$ be the centroid of the
    visible points around p. The normal $\vec{n}$ is defined as the first
    eigenvector of the covariance matrix \Nu of the visible points:
    \begin{equation}
        \Nu = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
    \end{equation}
    In order to reorient the normal, we use the trivial normal of the
    surface as a reference.

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{environ}
\usepackage{bbm}

@@

    In order to compute the visibility, we first compute $\Omega = \text{Star}(C)$. Then for each primal direction of
    coordinates at most $r$, we look at all the possible positions this specific direction does link 2 visible points
    of the cell complex. In order to do so, for each shift in $\Omega$, we compute the positions where points are
    visible using the same method as presented in~\ref{fig:enter-label}.

@@

    Let $V$ the visibility around the point $p$, let $c$ be the centroid of the
    visible points around p. The normal $\vec{n}$ is defined as the first
    eigenvector of the covariance matrix $\mathcal{V}$ of the visible points:
    \begin{equation}
        \mathcal{V} = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
    \end{equation}
    In order to reorient the normal, we use the trivial normal of the
    surface as a reference.

    \begin{figure}
        \begin{center}
            \includegraphics[width=0.8\textwidth]{pictures/torus-knot-normal-estimation}
            \caption{Normal estimation on a torus knot using the visibility
            algorithm. The normals are colored according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$
                .}
            \label{fig:normal-estimation}
        \end{center}
    \end{figure}
